Competing Bandits: The Perils of Exploration under Competition

### 2018-09-02 paper/content/inverted_u.tex
small change

Next, to describe our results for temporary monopoly, we will
introduce the following notion of \textit{effective end of game
  (EEOG)} --- the last round $t$ such that the agent at round $(t-1)$
and the next agent around at $t$ choose different firms.

>>>>

Next, to describe our results for temporary monopoly, we will
introduce the notion of \textit{effective end of game (EEOG)} --- the
last round $t$ such that the agent at round $(t-1)$ and the next agent
around at $t$ choose different firms.
